\documentclass[12pt]{article}

\usepackage{amsmath}  % for cdot
\usepackage{changepage}  % for adjustwidth
\usepackage{geometry}  % for newgeometry
\usepackage{graphicx}  % for geometry
\usepackage{scrextend}  % for addmargin

\usepackage{nopageno}  % remove page numbers

\newgeometry{left=0.5in, right=0.5in, top=0.5in, bottom=0.5in}  % set page margins

\frenchspacing  % single space after sentence
\setlength{\parindent}{0pt}  % don't indent paragraphs
\setlength{\parskip}{0pt}  % skip lines between paragraphs
\renewcommand*\ttdefault{pcr} % make courier default mono font
\renewcommand{\familydefault}{\ttdefault} % use default mono font

% contact info
\newcommand{\contact}[3]{
  \begin{centering}
    \Large{\textbf{#1}}

    \large{#2}

    \vspace{2pt}
    \normalsize{#3}

  \vspace{16pt}
  \end{centering}
}

% keywords info
\newcommand{\keywords}[1]{
  \general{
    \footnotesize{Keywords: #1}
  }
}

% topic of interest
\newcommand{\topic}[2]{ % name, content

  \vspace{16pt}
  \textmd{#1}

  \vspace{4pt}
  #2
}

% general item
\newcommand{\general}[1]{ % content

  \vspace{4pt}
  \begin{adjustwidth}{20pt}{0pt}
    \small{#1}
  \end{adjustwidth}
}

% detail item
\newcommand{\detail}[1] { % content

    \begin{adjustwidth}{4pt}{20pt}
      #1
    \end{adjustwidth}  
}

% experience item
\newcommand{\experience}[3]{ % heading, subheading, date
  \general{
    \small{#1} \hfill \footnotesize{#3}
    \detail{#2}
  }
}

% experience item
\newcommand{\bigexperience}[4]{ % heading, subheading, date, content
  \general{
    \small{#1} \hfill \footnotesize{#3}
    \detail{
      #2
    
      \vspace{4pt}
      \footnotesize{#4}
    }
  }
}

\begin{document}

\contact{Trevor Samson}
{tsamson@google.com}
{(781) 572-9527}

\keywords{
  Software systems, machine learning, data processing, community effects.
}

\topic{Education}
{
  \experience{Cornell University, College of Engineering}
  {B.Sc. in Engineering Physics, \textit{cum laude}}
  {May, 2015}

  \experience{Winchester High School, Massachusetts}
  {High school diploma}
  {June, 2011}
}

\topic{Software Engineering}
{
  \bigexperience{Google Books}
  {Google, Alphabet Inc.}
  {July 2017 - Present}
  {Backend ML and NLP for keyword extraction. Frontend and UI.}

  \bigexperience{Android Things}
  {Google, Alphabet Inc.}
  {Aug. 2016 - July 2017}
  {Adapting ML models for low-compute devices. Data pipelines.}

  \bigexperience{Nest Algorithms}
  {Nest Labs, Alphabet Inc.}
  {Sept. 2015 - Aug. 2016}
  {Cloud ML for data collected across distributed IoT devices.}
}

\topic{Research}
{
  \bigexperience{Research Affiliate}
  {MIT, Laboratory for Nuclear Science}
  {May - Aug. 2013, 2014}
  {Statistical analysis of large CERN datasets.}

  \bigexperience{Undergraduate Researcher}
  {Cornell University, LASSP}
  {Sept. 2013 - May 2014}
  {QED simulations to predict material properties.}
}

\topic{Community}
{
  \experience{Greenstar Cooperative Market}
  {Ithaca, NY}
  {Apr. 2015 - Sept. 2015}

  \experience{Mathematical Physics II, Teaching Assistant}
  {Cornell University, College of Engineering}
  {Jan. 2015 - May 2015}

  \experience{Watermargin Cooperative, President}
  {Cornell University}
  {Aug. 2014 - May 2015}
}

\topic{Skills}
{
  \general{
    Java Python SQL Javascript C++ \LaTeX{}
    {  }$\cdot${  }
    BigQuery DataFlow TensorFlow Pandas
  }
}

\end{document}

\topic{Community}
{
  \experience{Data for Black Lives}
  {MIT Media Lab}
  {Nov. 2017}

  \experience{Hacking Hemophilia}
  {MIT Hacking Medicine}
  {Oct. 2017}

  \experience{Research @}
  {Google}
  {Nov. 2016}
}
